### 2008-12-20 talk/ecoop2009/jitgen.tex
make sources a bit smaller, and comment out a big image which is not referenced by the text
fix few XXXs

\begin{figure}[h]
\begin{center}
\includegraphics[width=.6\textwidth]{diagram1}
\caption{PyPy infrastructure for generating an interpreter of a
  language $L$ with JIT compilation for the .NET platform}
\end{center}
\end{figure}

@@

XXX write something about the problems of classical PE?

@@

XXX need better transition text from last section
At translation time, PyPy performs binding-time analysis of the source
RPython program after it has been turned to low-level graphs, i.e. at
the level at which operations manipulate objects that have a fixed type
attached.

The binding-time terminology that we are using in PyPy is based on the
colors that we use when displaying the control flow graphs:

@@

The binding-time analyzer of our translation tool-chain is using a simple
abstract-interpretation based analysis. It is based on the
same type inference engine that is used on the source RPython program.
This is called the \emph{hint-annotator}; it
operates over input graphs that are already low-level instead of
RPython-level, \anto{we never make distinction between low-level and rpython-level 
flowgraphs, do we? I propose to talk about ``intermediate flowgraphs''} 
and propagates annotations that do not track types but
value dependencies and manually-provided binding time hints.

>>>>

\commentout{
\begin{figure}[h]
\begin{center}
\includegraphics[width=.6\textwidth]{diagram1}
\caption{PyPy infrastructure for generating an interpreter of a
  language $L$ with JIT compilation for the .NET platform}
\end{center}
\end{figure}
}

@@

@@

At translation time, PyPy performs binding-time analysis of the source
RPython program.  The binding-time terminology that we are using in PyPy is based on the
colors that we use when displaying the control flow graphs:

@@

The binding-time analyzer of our translation tool-chain is using a simple
abstract-interpretation based analysis. It is based on the
same type inference engine that is used on the source RPython program.
This is called the \emph{hint-annotator}; it
operates over input flowgraphs
and propagates annotations that do not track types but
value dependencies and manually-provided binding time hints.
